\vspace{-2.0cm}Stuff

### 2014-05-31 report/draft3.tex
Last graph and table modifications.
Some extra text discussing the new tables.
corrected old tables with new sim values.

	\includegraphics[width=\textwidth]{../images/Emp_Vs_Hnorm.pdf}
	\caption{1000 Simulations, Empirical vs Half-normal Detection function, for three different layouts. Dashed line equals true value of 20 objects per km$^2$\label{fig:sim1}}

@@

Table~\ref{table:sim1} supports what we observe in the histogram: the means vary between our two $g(r)$ options, but are approximately the same within the each option, regardless of which VCP layout we have chosen. 
\begin{table}[h]
	\caption{Empirical vs. Half-normal detection function, across all three layouts. 1000 simulations. True density 20/km$^2$}
	\begin{tabular}{ r r r r r r r r r}
	   $g(x)$	 & Layout		& Mean	& Std Dev	& LB 95 & UB 95	& 25th	& Median	&  75th \\ \hline \hline
	   Empirical & Random		& 14.52 & 3.35 		& 7.97	& 21.08	& 12.17	& 14.46	& 16.74\\
	   Empirical & Structured	& 14.50 & 3.22 		& 8.19 	& 20.81 & 12.38 & 14.45 & 16.62\\
	   Empirical & Transect		& 14.46 & 3.53 		& 7.55 	& 21.37 & 11.85 & 14.36 & 16.88\\ \hline
	 Half-normal & Random 		& 18.17 & 4.50 		& 9.34 	& 27.00 & 15.24 & 17.94 & 21.00\\
	 Half-normal & Structured	& 17.94 & 4.29 		& 9.54 	& 26.35 & 15.19 & 17.67 & 20.78\\
	 Half-normal & Transect		& 18.04 & 4.49 		& 9.23 	& 26.84 & 14.90 & 17.75 & 20.74\\

	\end{tabular}
	\label{table:sim1}
\end{table}

\texttt{TO DO: return T/F if the true value was contained in the interval. redo graph to match others.}

@@

\end{figure}
\begin{table}
	\caption{Half-normal detection function, three layouts, three movement types. 1000 simulations.}
	\begin{tabular}{ r| r r| r r| r r|}

@@

	\end{tabular}
	\label{table:sim2}
\end{table}

Figure~\ref{fig:sim2} and Table~\ref{table:sim2} illustrate the results of our movement type simulation. For this run, only the half-normal detection function was used.

Within a column, the results are fairly similar in shape and spread. We see the most obvious differences here between columns, indicating that the type of movement causes more bias in our estimate than the potential overlap of our observation areas.

Unexpectedly, the type of movement, temporary or permanent, does not seem to play a large part in changing the bias. Table~\ref{table:sim2} shows that the 95\% confidence intervals \parencite{quang1993} capture the true mean about 59\% of the time, no matter which movement type, Temporary or Compounded.

@@

The combination of compounded movement and the transect layout seems to have an effect on the density estimate. The other estimates for either movement type, are all in the same ballpark, around 11.8 with around a 59\% rate for capturing the true population value. For the Transect Layout and Compounded movement, this rises 0.50 to a mean population density estimate of 12.42, and a capture percent of 65\%. It is unclear if there is something about this combination that is reducing bias (possible, but feels unlikely), or if it is instead biasing the estimate upwards, which appears like bias reduction because the estimate is already low.

@@

>>>>

	\includegraphics[width=\textwidth]{../images/Emp_Vs_Hnorm_1-2.pdf}
	\caption{1000 Simulations, Empirical vs Half-normal Detection function, for three different layouts. Dashed line equals true value of 20 objects per km$^2$\label{fig:sim1}}

@@

Table~\ref{table:sim1} supports what we observe in the histogram: the centers vary between our two $g(r)$ options, but are approximately the same within the each option, regardless of which VCP layout we have chosen. Table~\ref{table:sim1capture} shows the percentage of simulations that captured the true object density of 20 per km$^2$ within a 95\% confidence interval. \cite{quang1993}

There may be evidence of a drop in accuracy with the Transect layout, but it is difficult to determine if this is a valid observation, or an artifact of this particular simulation. The drop, if it exists, is much less severe with the half-normal detection function. With the empirical detection function, the structured layout percentage swings much higher than the result from our random layout, unlike for half-normal where they are just over 1\% apart. Repeated simulations, could help narrow down if this is a true effect, or simply random noise.
\begin{table}[h]

	\begin{tabular}{ r r |r r| r r r}
		$g(x)$      & Layout     & Mean  & Std Dev & 25th  & Median & 75th  \\ \hline\hline
		Empirical   & Random     & 14.47 & 3.37    & 12.08 & 14.38  & 16.73 \\
		Empirical   & Structured & 14.49 & 3.15    & 12.27 & 14.47  & 16.59 \\
		Empirical   & Transect   & 14.26 & 3.66    & 11.65 & 14.14  & 16.80 \\ \hline
		Half-normal & Random     & 17.90 & 4.57    & 14.67 & 17.86  & 20.88 \\
		Half-normal & Structured & 18.03 & 4.16    & 15.05 & 17.91  & 20.82 \\
		Half-normal & Transect   & 17.80 & 4.64    & 14.52 & 17.44  & 20.78
	\end{tabular}
	\caption{Centers and Spread for Empirical vs. Half-normal detection functions. 1000 simulations. True density 20/km$^2$}
	\label{table:sim1}
\end{table}
\begin{table}[h]

	\begin{tabular}{ r| r r| r r|}
		           & \multicolumn{2}{|c|}{Empirical} & \multicolumn{2}{|c|}{Half Normal} \\ \hline\hline
		Layout     & Mean $\hat{D}$ & \% Capture     & Mean $\hat{D}$ & \% Capture       \\ \hline\hline
		Random     & 14.47          & 73.6\%         & 17.90          & 94.0\%           \\
		Structured & 14.49          & 77.5\%         & 18.03          & 95.3\%           \\
		Transect   & 14.27          & 69.6\%         & 17.80          & 91.2\%           \\ \hline
	\end{tabular}
	\caption{True Density Capture, Emperical vs. Half-normal detection function for three layouts. 1000 simulations.}
	\label{table:sim1capture}
\end{table}

@@

\end{figure}
\begin{table}[h]

	\begin{tabular}{ r r| r r| r r r}
		Movement  & Layout     & Mean  & Std Dev & 25th  & Median & 75th  \\ \hline\hline
		None      & Random     & 17.86 & 4.28    & 15.03 & 17.64  & 20.65 \\
		None      & Structured & 18.01 & 4.51    & 14.95 & 17.62  & 20.94 \\
		None      & Transect   & 17.90 & 4.78    & 14.74 & 17.67  & 20.95 \\ \hline
		Permanent & Random     & 11.86 & 3.42    & 9.58  & 11.61  & 14.09 \\
		Permanent & Structured & 11.90 & 3.65    & 9.37  & 11.67  & 14.08 \\
		Permanent & Transect   & 12.42 & 3.72    & 9.93  & 12.17  & 14.79 \\ \hline
		Temporary & Random     & 11.76 & 3.57    & 9.22  & 11.75  & 14.02 \\
		Temporary & Structured & 11.74 & 3.48    & 9.37  & 11.56  & 13.85 \\
		Temporary & Transect   & 11.75 & 3.57    & 9.24  & 11.72  & 14.20
	\end{tabular}
	\caption{Centers and Spread for Movement and Layout combinations. 1000 simulations. True density 20/km$^2$}
	\label{table:sim2}
\end{table}
\begin{table}

	\begin{tabular}{ r| r r| r r| r r|}

@@

	\end{tabular}
	\caption{Mean and Capture Rate, Half-normal detection function, three layouts, three movement types. 1000 simulations.}
	\label{table:sim2capture}
\end{table}

Figure~\ref{fig:sim2} and Tables~\ref{table:sim2} and~\ref{table:sim2capture} illustrate the results of our movement type simulation. For this run, only the half-normal detection function was used.

For testing combinations of movement and VCP layout, only the half-normal detection function was utilized. Figure~\ref{fig:sim} compares the histograms of the nine combinations. On the whole, the estimates are biased low, as was observed in the previous simulation, without movement. Within a column, the results are fairly similar in shape and spread. The most obvious differences lie between columns, indicating that the type of movement causes more bias in our estimate than the potential overlap of our observation areas.

Table~\ref{table:sim2} reinforces this conclusion, as the measures of center and spread are reasonably consistent within Movement type, regardless of the VCP Layout. Differences are observed between movement types, with No Movement having the estimates with the smallest amount of downward bias, and Compounded and Temporary movement biasing the population density estimate about the same amount.

Unexpectedly, the type of movement, temporary or permanent, does not seem to play a large part in changing the bias. Table~\ref{table:sim2capture} shows that the 95\% confidence intervals \parencite{quang1993} capture the true mean about 59\% of the time, no matter which movement type, Temporary or Compounded.

@@

The combination of compounded movement and the transect layout seems to have an effect on the density estimate. The other estimates for either movement type, are all in the same ballpark, around 11.8 with an approximate 59\% rate for capturing the true population value. For the Transect Layout and Compounded movement, this rises 0.50 to a mean population density estimate of 12.42, and a capture percent of 65\%. It is unclear if there is something about this combination that is reducing bias (possible, but feels unlikely), or if it is instead biasing the estimate upwards, which appears like bias reduction because the estimate is already low.

@@

There is a possible effect of the combination of compounded movement and the transect layout. It is unclear from these results what the particular cause of the increased estimate and accuracy is. Future work might involve modification of the simulation functions to return more information, such as the count of observed animals and the observation distances to assist with understanding why this combination is producing an estimate that appears out of line with it's neighbors.
